A survey of HTTP caching options on the open Web

### 2014-12-16 sanity/paper1.tex
some related work
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@901 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\section{Related work}

We are not aware of any surveys of this type. Although the database
literature is rich with query cache literature, it is mostly relevant
to what would happen within the server or between the server and a
reverse proxy, which is opaque to the Internet, and therefore not of
our concern.

LDF\todo{ref paper1} claims to take advantage of caching and contrasts
this with the inavailabilty of SPARQL query caches, and claims this is
an architectural problem.

The implications of HTTP for query caches has been discussed by
\todo{ref kasei}. In \todo{marin, Auer} the authors implemented a
reverse proxy that controlled the changes to the dataset, and
therefore could

A general caching approach is given in \todo{Caching intermediate
  result of sparql queries}.

\todo{fast vs. fresh} didn't consider caching in the sense we do, they
rather prefetch an entire dataset to a local store and based on
heuristics tried to determine which parts of the query should be
evaluated remotely and locally.

\todo{cache or not} explored when caching had a positive effect on
complex SPARQL queries.

In the broader Web literature, \todo{Revisiting Cacheability
in Times of User Generated Content} analysed the value of caching
based anonymized traces of actual Web usage at a major Internet
Service Provider.
